Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/abstract.tex
working on the abstract

>>>>

A staged program is a program where expressions are assigned to a
stage corresponding to their order of evaluation.  For example, in a
two-staged program, some of the inputs become available in stage-1 and
others in stage-2.  Evaluation of such a program proceeds by
evaluating all the stage-1 expressions to construct a stage-2
expression, which is then evaluated in stage-2.  Programming
languages, evaluation strategies, and type systems for staged programs
have been studied extensively by the research on partial evaluation
and meta programming.

In this paper, we consider a relatively less considered evaluation
strategy for staged programs by splitting a staged program into a
multiple passes, where each pass corresponds to a stage of evaluation.
For example, a 2-stage program would be split into two programs pass-1
and pass-2, one for each phase, and evaluation proceeds by evaluating
proceeds by evaluating pass-
